Supporting Information: Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling.

### 2020-01-23 Ben_Manuscripts/stochastic_transport/Supporting_Information.tex
Incorporated MRS comments

  % mimic this
  \texttt{/setup/parameterize.py}            & 2.1 & Parameterize liquid crystal monomers and solutes with GAFF \\ \hline
  \texttt{/setup/build.py}                   & 2.1 & Build simulation unit cell \\ \hline
  \texttt{/setup/place\_solutes\_pores.py}   & 2.1 & Place equispaced solutes in the pore centers of a unit cell \\\hline
  \texttt{/setup/equil.py}                   & 2.1 & Equilibrate unit cell and run production simulation \\\hline
  \texttt{/analysis/solute\_partitioning.py} & 2.1 & Determine time evolution of partition of solutes between pores and tails \\\hline
  \texttt{/timeseries/msd.py}                & 2.2 & Calculate the mean squared displacement of solutes \\\hline
  \texttt{/analysis/sfbm\_parameters.py}     & 2.2 & Get subordinated fractional Brownian motion parameters by fitting to a solute's dwell and hop length distributions and positional autocorrelation function. \\\hline
  \texttt{/timeseries/ctrwsim.py}            & 2.2 & Generate realizations of a continuous time random walk with the user's choice of dwell and hop distributions \\\hline
  \texttt{/timeseries/forecast\_ctrw.py}     & 2.2 & Combines classes from \texttt{sfbm\_parameters.py} and \texttt{ctrwsim.py} to parameterize and predict MSD in one shot. \\\hline
  \texttt{/analysis/ Markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
  \texttt{/timeseries/mfpt\_pore.py}          & 2.4 & Simulate mean first passage time distributions using the AD or MSDDM model. \\\hline
%MRS8: see main text discussion about ``the XXXX model''  
  \end{tabular}

@@

  % /supporting_figures/hurst_autocorrelation.py
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{hurst_autocorrelation.pdf}
  \caption{}\label{fig:hurst_autocorrelation}
  \end{subfigure}
  % supporting_figures/flm_autocov.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flm_autocovariance.pdf}
  \caption{}\label{fig:flm_autocorrelation}
  \end{subfigure}
  %MRS8: make clear in (b) the lines all lay on top so people don't miss it.  
  \caption{(a) The analytical autocorrelation function of FBM decays to zero faster
  when H $<$ 0.5 compared to when H $>$ 0.5. (b) The autocorrelation function of an 
  FLM process does not change with increasing sequence length (N). It shares the same
  autocorrelation function as fractional Brownian motion (FBM). All 
  %sequenced
  sequences 
  used to
  make this plot were generated using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:hurst_parameters}
  \end{figure}

@@

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (1 mode)}\label{fig:1mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (2 modes)}\label{fig:2mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (1 mode)}\label{fig:1mode_msd_comparison_ACH_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (2 modes)}\label{fig:2mode_msd_comparison_ACH_train_front}
  \end{subfigure} 
  %MRS6: I'm not sure I see red in urea.  Is the uncertainty that low?
  %BJC6: I think red and orange are directly on top of each other with same error bars
  %MRS8: point out that the _cut data is the same as the data in the main tex. 
  \caption{In most cases, when using power laws with exponential cut-offs 
  (sFBMcut and sFLMcut), the MSD curves predicted by the AD model trained on 
  the first half of the equilibrated data lie within the 1$\sigma$ confidence
  intervals of the MD MSD curves generated from the second half of the equilibrated
  solute data. The models which use pure power laws systematically under-predict
  the MD MSD curves. Over- and under-estimated curvature of the of urea and acetic acid's 
  MSD curves respectively causes the magnitude of urea's predicted MSDs to be 
  under-predicted at long timescales and those of acetic acid to be under-predicted
  at short timescales.}\label{fig:train_test}
  \end{figure}

  The models are capable of reasonably predicting the MD MSD values of the second
  half of the solute trajectories based on parameters generated from the first half
  when the dwell time distributions are parameterized by a power law with an 
  exponential cut-off. At long timescales, the MSD of urea is under-predicted 
  for both the 1 and 2 mode models with the same true of acetic acid on short 
  timescales. Without truncation of the power law distribution, the MD 
  MSDs are underestimated in all cases because dwell times on the order of the
  MD simulation length are sampled and incorporated into the simulated anomalous
  diffusion trajectories. Considering the longest observed dwell time among all
  solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
  %Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
  %intervals of the MD MSD curves, they appear to lie systematically below the mean. 
  %It is not clear whether this is a consistent feature of the AD model since we 
  %only used 2 solutes for this analysis.

@@

  From a qualitative perspective, the models only have moderate success at predicting
  the shape of the MSD curves. Error in the MSD curvature can also help explain some of
  the error in the predicted MSD magnitudes. The curves predicted for urea with both 1 
  and 2 modes appear to have too much curvature, which causes it to under-predict the 
  MSD at long timescales, while those of acetic acid lack curvature, leading the
  AD model to under-predict the MSD at short timescales.

  %MRS8: how much of this is already in the main text?  Try to limit analysis that appears in the main text.
  The under-estimate of urea's MSD at long timescales is due to long timescale
  positional anti-correlation which may not be present in the molecularly 
  detailed simulations of the system. The 
  %MRS6: I'm not following whether or not there should be positional anti-correlation.  I was thinking there should be,
  %but perhaps I'm misunderstanding something here? 
  persistent curvature of the predicted MSD curves is a direct consequence of 
  the Hurst parameter. Without anti-correlation, the process would be 
  a pure CTRW for which one would expect the time averaged MSD curves to become 
  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
  positional correlation is lost which would manifest as a transition from a sub-linear
  to linear MSD curve. A solution for more accurately modeling this behavior in  
  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}

  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
  because the Hurst parameter is challenging to quantify, especially with a relatively 
  small amount of data (see Section~\ref{M-method:sfbm} of the main text for further discussion of this 
  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
  but also lower the predicted MSD meaning we are either underestimating the width of
  the hop length distribution, favoring longer dwell times, or both.

  This brief qualitative analysis suggests two shortcomings of the AD model. First, in
  a real system, positional anti-correlation may dissipate after a sufficiently long 
  time lag, dependent on the solute being studied. Second, it is difficult to reliably
  parameterize the Hurst parameter which is important for accurately describing the 
  curvature of the solute MSDs.

  This analysis also suggests that working with only half of the data we collected
  ($\sim$ 2 $\mu$s post-equilibration) is not always sufficient for extracting reliable
  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
  sFLMcut), but still appear to systematically under-predict the mean. We may be
  operating on the border of the minimum amount of data required to accurately 
  parameterize the AD model. Longer simulations and more independent trajectories may
  be necessary. Therefore, in the next section we will work with parameters fit to the
  full equilibrated portion of the solute trajectories, doubling the data.

@@

  %MRS8: I think just ``Tables of Anomalous''.  Tabular sounds like it's a kind of anomalous diffusion.
  \section{Tabular Anomalous Diffusion Parameters}\label{section:tabular_AD_params}

  %MRS8: representations of the parameters, or representations of the graphs?  Or just tabulations of the data found in the graph.
  The tables in the section are tabular representations of the parameters depicted
  in Figures~\ref{M-fig:1mode_parameters} and~\ref{M-fig:2mode_parameters} of the 
  main text.

  % BJC: note to self -- modes are flipped in simulation output because 
  % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0. 
  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol &   Methanol   & Acetic Acid  \\\hline
  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            & 0.62         & 0.45         \\\cline{2-6}
  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    & 0.44, 0.0040 & 0.08, 0.0033 \\\hline
  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            & 0.35         & 0.27         \\\cline{2-6}
  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      & 0.22, 1.80   & 0.16, 1.72   \\\hline
  Correlation   & $\gamma(H)$               & 0.37         & 0.40            & 0.30         & 0.34         \\
  \hline 
  \end{tabular}
  %MRS: to what extent are these captions the same as the captions to equivalent graphs main text?  If it's the same, you probably should say so; if different, there should be some justification for the differences, and should be mentioned in the main text that more information is here. 
  \caption{To create a 1 mode model for each solute, we parameterized a pure power
  law ($P(\alpha_d)$) and a truncated power law ($P_T(\alpha_d, \lambda)$) distribution 
  to describe solute dwell times. Lower values of $\alpha_d$ lead to heavier power 
  law tails and higher values of $\lambda$ truncate the distribution at lower
  dwell times. We parameterized Gaussian ($\mathcal{N}(\sigma)$) and L\'evy stable 
  ($L(\sigma, \alpha_h)$) distributions to describe solute hop lengths. We assume
  the mean ($\mu$) to be zero for these distributions and there to be no skewness ($\beta=0$)
  in the L\'evy stable distributions. High values of $\sigma$ and lower values of
  $\alpha_h$ result in larger hops. Finally, we parameterized the hop autocorrelation
  function ($\gamma(H)$) to describe the degree of correlation between hops. 
  Higher values of $H$ display closer to Brownian behavior.}\label{table:sfbm_params}
  \end{table}

  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  \multicolumn{7}{|c|}{2 Mode Model} \\\hline
                & Parameters                               & Mode & Urea         & Ethylene Glycol &  Methanol    & Acetic Acid \\
  \hline
                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           & 0.90         & 0.58         \\\cline{3-7}
  Dwell         &                                          & 2    & 0.38         &  0.48           & 0.58         & 0.33         \\\cline{2-7}
  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   & 1.04, 0.0006 & 0.41, 0.0026 \\\cline{3-7}
                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   & 0.30, 0.0054 & 0.00, 0.0021 \\\hline
                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           & 0.45         & 0.32         \\\cline{3-7}
  Hop           &                                          & 2    & 0.24         &  0.23           & 0.32         & 0.17         \\\cline{2-7}
  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     & 0.31, 1.97   & 0.21, 1.91   \\\cline{3-7}
                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     & 0.20, 1.85   & 0.09, 1.50   \\\hline
  Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           & 0.30         & 0.34         \\\cline{3-7}
  \hline 
  \end{tabular}
  \caption{The two model parameterizes solute behavior in the pores and tails separately. 
  Generally, movement is much more restricted in the tail region. To create a 2 mode model,
  we generated a set of parameters based on solute behavior as function of distance from
  the pore center. Mode 1 corresponds to solute behavior within 0.75 nm of the pore center
  and mode 2 corresponds to behavior greater than or equal to 0.75 nm from the pore center.
  Note that we used the same Hurst parameter for both modes due to a low number of 
  sufficiently long sequences of hops in each mode. See Table~\ref{table:sfbm_params} for
  descriptions of the parameters.}\label{table:sfbm_params_2mode}
  \end{table}

  \newpage
  %MRS8: ``Table of''. Same comments about captions being the same or different, since the data should be the same.
  \section{Tabular MSDDM parameters}\label{section:msddm_params}

@@

  %MRS8: See discussion in main text on ``the AD model''
  %MRS8: fig:msddm_fpt_fits is commented out?  Or xr not working should this be main text?
  In Figures~\ref{fig:ad_fpt_fits} and~\ref{fig:msddm_fpt_fits}, we demonstrate
  the high quality of our analytical fits of Equation~\ref{eqn:passage_times} to 
  the distribution of solute first passage times derived from both the AD
  and MSDDM models. The histograms in Figure~\ref{fig:msddm_fpt_fits} are 
  relatively noisy because we only generated 1000 realizations of the MSDDM 
  versus 10000 of the AD model. In Figure~\ref{fig:flux_curve_sensitivity}, we
  justify our use of fewer MSDDM realizations by using subsets of the 10000 AD 
  model realizations to show that one needs as few as 100 independent trajectory
  realizations at each pore length in order to reliably fit Equation~\ref{eqn:passage_times}
  to the passage time distributions.

>>>>

  % mimic this
  \texttt{/setup/parameterize.py}            & 2.1 & Parameterize liquid crystal monomers and solutes with GAFF \\ \hline
  \texttt{/setup/build.py}                   & 2.1 & Build simulation unit cell \\ \hline
  \texttt{/setup/place\_solutes\_pores.py}   & 2.1 & Place equispaced solutes in the pore centers of a unit cell \\\hline
  \texttt{/setup/equil.py}                   & 2.1 & Equilibrate unit cell and run production simulation \\\hline
  \texttt{/analysis/solute\_partitioning.py} & 2.1 & Determine time evolution of partition of solutes between pores and tails \\\hline
  \texttt{/timeseries/msd.py}                & 2.2 & Calculate the mean squared displacement of solutes \\\hline
  \texttt{/analysis/sfbm\_parameters.py}     & 2.2 & Get subordinated fractional Brownian motion parameters by fitting to a solute's dwell and hop length distributions and positional autocorrelation function. \\\hline
  \texttt{/timeseries/ctrwsim.py}            & 2.2 & Generate realizations of a continuous time random walk with the user's choice of dwell and hop distributions \\\hline
  \texttt{/timeseries/forecast\_ctrw.py}     & 2.2 & Combines classes from \texttt{sfbm\_parameters.py} and \texttt{ctrwsim.py} to parameterize and predict MSD in one shot. \\\hline
  \texttt{/analysis/ Markov\_state\_dependent\_dynamics.py} & 2.3 & Identify frame-by-frame state of each solute, construct a transition matrix and simulate realizations of the MSDDM model. \\\hline
  \texttt{/timeseries/mfpt\_pore.py}          & 2.4 & Simulate mean first passage time distributions using the AD approach. \\\hline 
  \end{tabular}

@@

  % /supporting_figures/hurst_autocorrelation.py
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{hurst_autocorrelation.pdf}
  \caption{}\label{fig:hurst_autocorrelation}
  \end{subfigure}
  % supporting_figures/flm_autocov.py
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{flm_autocovariance.pdf}
  \caption{}\label{fig:flm_autocorrelation}
  \end{subfigure}  
  \caption{(a) The analytical autocorrelation function of FBM decays to zero faster
  when H $<$ 0.5 compared to when H $>$ 0.5. (b) The autocorrelation function of an 
  FLM process does not change with increasing sequence length (N). It shares the same
  autocorrelation function as fractional Brownian motion (FBM). Note that all lines
  plotted lie on top of each other. All sequences used to make this plot were generated
  using $H$=0.35 and, for FLM, $\alpha$=1.4.}\label{fig:hurst_parameters}
  \end{figure}

@@

  The models are capable of reasonably predicting the MD MSD values of the second
  half of the solute trajectories based on parameters generated from the first half
  when the dwell time distributions are parameterized by a power law with an 
  exponential cut-off. At long timescales, the MSD of urea is under-predicted 
  for both the 1 and 2 mode models with the same true of acetic acid on short 
  timescales. Without truncation of the power law distribution, the MD 
  MSDs are underestimated in all cases because dwell times on the order of the
  MD simulation length are sampled and incorporated into the simulated anomalous
  diffusion trajectories.

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (1 mode)}\label{fig:1mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_URE_train_front.pdf}
  \caption{Urea (2 modes)}\label{fig:2mode_msd_comparison_URE_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{1mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (1 mode)}\label{fig:1mode_msd_comparison_ACH_train_front}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{2mode_msd_comparison_ACH_train_front.pdf}
  \caption{Acetic acid (2 modes)}\label{fig:2mode_msd_comparison_ACH_train_front}
  \end{subfigure} 
  \caption{In most cases, when using power laws with exponential cut-offs 
  (sFBMcut and sFLMcut), the MSD curves predicted by the AD model trained on 
  the first half of the equilibrated data lie within the 1$\sigma$ confidence
  intervals of the MD MSD curves generated from the second half of the equilibrated
  solute data. The models which use pure power laws systematically under-predict
  the MD MSD curves. Over- and under-estimated curvature of the of urea and acetic acid's 
  MSD curves respectively causes the magnitude of urea's predicted MSDs to be 
  under-predicted at long timescales and those of acetic acid to be under-predicted
  at short timescales. Note that the sFBMcut and sFLMcut models are the same as 
  those in the main text.}\label{fig:train_test}
  \end{figure}

  %Considering the longest observed dwell time among all
  %solutes was 1.3 $\mu$s by ethylene glycol, we believe truncation is well-justified.
  %Although in most cases, the predicted MSD curves overlap the 1-$\sigma$ confidence
  %intervals of the MD MSD curves, they appear to lie systematically below the mean. 
  %It is not clear whether this is a consistent feature of the AD model since we 
  %only used 2 solutes for this analysis.

@@

%  From a qualitative perspective, the models only have moderate success at predicting
%  the shape of the MSD curves. Error in the MSD curvature can also help explain some of
%  the error in the predicted MSD magnitudes. The curves predicted for urea with both 1 
%  and 2 modes appear to have too much curvature, which causes it to under-predict the 
%  MSD at long timescales, while those of acetic acid lack curvature, leading the
%  AD model to under-predict the MSD at short timescales.

  %MRS8: how much of this is already in the main text?  Try to limit analysis that appears in the main text.
%  The under-estimate of urea's MSD at long timescales is due to long timescale
%  positional anti-correlation which may not be present in the molecularly 
%  detailed simulations of the system. The 
%  persistent curvature of the predicted MSD curves is a direct consequence of 
%  the Hurst parameter. Without anti-correlation, the process would be 
%  a pure CTRW for which one would expect the time averaged MSD curves to become 
%  linear.~\cite{meroz_toolbox_2015} It may be true that on the $\mu$s time scale, 
%  positional correlation is lost which would manifest as a transition from a sub-linear
%  to linear MSD curve. A solution for more accurately modeling this behavior in  
%  the future may be to truncate the positional autocorrelation function.~\cite{molina-garcia_crossover_2018}
%  
%  The under-estimate of the curvature of acetic acid's predicted MSD suggests that,
%  in this case, the AD model over-estimates the Hurst parameter. This is not surprising
%  because the Hurst parameter is challenging to quantify, especially with a relatively 
%  small amount of data (see Section~\ref{M-method:sfbm} of the main text for further discussion of this 
%  challenge). A more accurate measurement of $H$ would fix the shape of the MSD curve,
%  but also lower the predicted MSD meaning we are either underestimating the width of
%  the hop length distribution, favoring longer dwell times, or both.
%  
%  This brief qualitative analysis suggests two shortcomings of the AD model. First, in
%  a real system, positional anti-correlation may dissipate after a sufficiently long 
%  time lag, dependent on the solute being studied. Second, it is difficult to reliably
%  parameterize the Hurst parameter which is important for accurately describing the 
%  curvature of the solute MSDs.
%  
%  This analysis also suggests that working with only half of the data we collected
%  ($\sim$ 2 $\mu$s post-equilibration) is not always sufficient for extracting reliable
%  parameter estimates. In most cases, the magnitude of the MSD predictions after a 
%  500 ns time lag are within or close to within error of the MD MSDs (for sFBMcut and
%  sFLMcut), but still appear to systematically under-predict the mean. We may be
%  operating on the border of the minimum amount of data required to accurately 
%  parameterize the AD model. Longer simulations and more independent trajectories may
%  be necessary. Therefore, in the next section we will work with parameters fit to the
%  full equilibrated portion of the solute trajectories, doubling the data.

@@

  \clearpage

  \section{Tables of Anomalous Diffusion Parameters}\label{section:tabular_AD_params}

  %MRS8: representations of the parameters, or representations of the graphs?  Or just tabulations of the data found in the graph.
  The tables in this section are tabular representations of the parameters depicted in
  Figures~\ref{M-fig:1mode_parameters} and~\ref{M-fig:2mode_parameters} of the main text
  and used to generate AD approach realizations whose MSDs are shown in Figure~\ref{M-fig:anomalous_msds}
  of the main text.

  % BJC: note to self -- modes are flipped in simulation output because 
  % physical.partition() sets mode as booleans and when r <= 0.75, in-pore is True (1) instead of 0. 
  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  1 Mode Model  & Parameters                & Urea         & Ethylene Glycol &   Methanol   & Acetic Acid  \\\hline
  Dwell         & $P(\alpha_d)$             & 0.57         & 0.62            & 0.62         & 0.45         \\\cline{2-6}
  Distributions & $P_T(\alpha_d, \lambda)$  & 0.40, 0.0024 & 0.47, 0.0030    & 0.44, 0.0040 & 0.08, 0.0033 \\\hline
  Hop           & $\mathcal{N}(\sigma)$     & 0.33         & 0.34            & 0.35         & 0.27         \\\cline{2-6}
  Distributions & $L(\sigma, \alpha_h)$     & 0.21, 1.84   & 0.23, 1.92      & 0.22, 1.80   & 0.16, 1.72   \\\hline
  Correlation   & $\gamma(H)$               & 0.37         & 0.40            & 0.30         & 0.34         \\
  \hline 
  \end{tabular}
  \caption{Parameters of the one mode AD approach models. See the main
  text for further details.}\label{table:sfbm_params}
  \end{table}

  \begin{table}[h]
  \centering
  \begin{tabular}{|M{2cm}|M{1.65cm}|M{.75cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|M{1.95cm}|}
  \hline
  \multicolumn{7}{|c|}{2 Mode Model} \\\hline
                & Parameters                               & Mode & Urea         & Ethylene Glycol &  Methanol    & Acetic Acid \\
  \hline
                &\multirow{2}{*}{$P(\alpha_d)$}            & 1    & 0.69         &  0.69           & 0.90         & 0.58         \\\cline{3-7}
  Dwell         &                                          & 2    & 0.38         &  0.48           & 0.58         & 0.33         \\\cline{2-7}
  Distributions &\multirow{2}{*}{$P_T(\alpha_d, \lambda)$} & 1    & 0.56, 0.0037 &  0.62, 0.0026   & 1.04, 0.0006 & 0.41, 0.0026 \\\cline{3-7}
                &                                          & 2    & 0.00, 0.0027 &  0.06, 0.0049   & 0.30, 0.0054 & 0.00, 0.0021 \\\hline
                &\multirow{2}{*}{$\mathcal{N}(\sigma)$}    & 1    & 0.35         &  0.38           & 0.45         & 0.32         \\\cline{3-7}
  Hop           &                                          & 2    & 0.24         &  0.23           & 0.32         & 0.17         \\\cline{2-7}
  Distributions &\multirow{2}{*}{$L(\sigma, \alpha_h)$}    & 1    & 0.24, 1.91   &  0.26, 1.99     & 0.31, 1.97   & 0.21, 1.91   \\\cline{3-7}
                &                                          & 2    & 0.12, 1.50   &  0.15, 1.90     & 0.20, 1.85   & 0.09, 1.50   \\\hline
  Correlation   & $\gamma(H)$                              & --   & 0.37         &  0.40           & 0.30         & 0.34         \\\cline{3-7}
  \hline 
  \end{tabular}
  \caption{Parameters of the 2 mode AD approach models. See the main text for further
  details.}\label{table:sfbm_params_2mode}
  \end{table}

  \newpage
  \section{Table of MSDDM parameters}\label{section:msddm_params}

@@

  %MRS8: See discussion in main text on ``the AD model''
  %MRS8: fig:msddm_fpt_fits is commented out?  Or xr not working should this be main text?
  %BJC8: yeah because 
  In Figure~\ref{fig:ad_fpt_fits} 
  %and~\ref{fig:msddm_fpt_fits},  % BJC8: didn't do solute flux with MSDDM so why mention
  we demonstrate
  the high quality of our analytical fits of Equation~\ref{eqn:passage_times} to 
  the distribution of solute first passage times derived from both the AD
  and MSDDM models. 
  %The histograms in Figure~\ref{fig:msddm_fpt_fits} are 
  %relatively noisy because we only generated 1000 realizations of the MSDDM 
  %versus 10000 of the AD model. 
  In Figure~\ref{fig:flux_curve_sensitivity}, we
  %justify our use of fewer MSDDM realizations by using subsets of the 10000 AD 
%  model realizations to 
  show that one only needs as few as 100 independent trajectory
  realizations at each pore length in order to reliably fit Equation~\ref{eqn:passage_times}
  to the passage time distributions.
